### 2017-04-13 sections/results.tex
Update on Overleaf.

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{figures/PSNR}
\caption{Comparison of Peek signal to noise ratio value calculated for different decompositions.}
\label{fig:PSNR}
\end{figure}

@@

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/temelin_ExecutionTime}
\caption{Variation of execution time of standard and randomized decompositions calculated for Temelin project results.}
\label{fig:temelin:ExeTime}
\end{figure}

>>>>

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/PSNR}
\caption{Comparison of Peek signal to noise ratio value calculated for different decompositions.}
\label{fig:PSNR}
\end{figure}

@@

\begin{figure}[H]
\centering\includegraphics[width=\textwidth]{figures/temelin_ExecutionTime}
\caption{Variation of execution time of standard and randomized decompositions calculated for Temelin analysis results.}
\label{fig:temelin:ExeTime}
\end{figure}

The memory consumption of compressed results for Temelin analysis is summarized in Table \ref{tab:mem-consum}. For different values of compression ratio shows memory size in megabytes. Compression ratio $c$ is an input parameter to the compression algorithm specifying amount of singular values ought to be removed from the SVD decomposition as follows from the equation (\ref{eq:rank-from-comp-ratio}). Size factor describes the final outcome of compression when compared to the original size.

\begin{table}[H]
\centering
    \begin{tabular}{| r | r | r |}
    \hline
    compression ratio ($c$) & memory consumption [MB] & size factor \\ \hline \hline
    1.00 & 2002.1 & 1 \\ \hline
    0.50 & 1006.9 & 0.5002 \\ \hline
    0.10& 211.9 & 0.1053 \\ \hline
    0.01 & 35.3 & 0.0176 \\ \hline
    \end{tabular}
    \caption{Memory consumption of compressed results. Temelin analysis.}
	\label{tab:mem-consum}
\end{table}
